Network Slicing and Resource Allocation in an Open RAN System \vspace{-.1cm}

### 2020-12-21 Latex/journal_v1/pr.tex
improve journal
journal complete

\textstyle \phi_{tot} = \sum_{s=1}^{S}\sum_{d=1}^{D_c}y_{s,d}\phi_{s,d} + \sum_{d=1}^{D_c}z_d \psi_d .

@@

@@

\min\limits_{\boldsymbol{P}, \boldsymbol{A}, \boldsymbol{B}, \boldsymbol{E}, \boldsymbol{G}, \boldsymbol{Y} }   \quad &  P_{tot}+ \varphi \phi_{tot} \ \\

@@

& \textstyle  \sum_{s=1}^{S}a_{v,s} \geq 1 \quad \forall s, \label{c21} \\

@@

\newpage
\newpage

Our goal is to maximize sum-rate and minimize sum-power (the total power of all RUs and the total power consumption of baseband processing at all DCs) simultaneously, with the presence of constraints which is written as follow,
\max\limits_{\boldsymbol{P}, \boldsymbol{A}, \boldsymbol{Y} }   \quad &  \eta(\boldsymbol{P},\boldsymbol{A})+ \varphi \frac{1}{\psi_{tot}(\boldsymbol{Y})} \\
\text{subject to} \quad  & \bar{p}_{r_{(s,i)}} \leq P_{max} \quad \forall s, \forall i,
&p_{u_{(v,k)}}  \geq 0  \quad \forall v, \forall k,\label{c12} \\
&\mathcal{R}_{u_{(v,k)}} \geq  \mathcal{R}_{u_{(v,k)}}^{min} \quad \forall v, \forall k,\label{c13} \\
&C_{r_{(s,i)}} \leq C_{r_{(s,i)}}^{max} \quad \forall s, \forall i, \label{c14}\\
&D_{s} \leq D_{s}^{max} \quad \forall s,\label{c15} \\
& \textstyle  \sum_{s=1}^{S}a_{v,s} \geq 1 \quad \forall s, \label{c21} \\
where $\boldsymbol{P} =[p_{u(v,k)}] \:\: \forall v , \forall k $, is the matrix of power for UEs, $\boldsymbol{A} =[a_{v,s}] \:\: \forall v , \forall s $ denotes the binary variable for connecting slices to services and $\boldsymbol{Y} =[y_{s,d}]  \:\: \forall s ,  \forall d $ is a binary variable shown whether
the physical DC is mapped to a VNFs of a slice or not.
Also, $\varphi$ is weighted variable to value between first and second term of objective function.
\eqref{c11}, and \eqref{c12}, indicate that the power of each RU do not exceed the maximum power, and the power of each UE is a positive integer value, respectively. Also \eqref{c13} shows that the rate of each UE is more than a threshold. \eqref{c14} and \eqref{c15} expressed the limited capacity of the fronthaul link, and the limited delay of receiving signal, respectively.
Furthermore, \eqref{c21}
ensures that each service is mapped to at least one slice.
Also, \eqref{c23}, guarantees that each slice (VNFs in two layers of slices) has been placed to one or more physical resources of DCs. Moreover, in \eqref{c22}  $\mathcal{E} = \{M,S,C\}$ and the constraint supports
that we have enough physical resources for VNFs of each slice.\newline
The optimization problem in \eqref{constraints} can be decomposed into two independent optimization sub-problems 1 and 2 since the variables can be obtained independently and respectively. Firstly we need to solve sub-problem 1. After obtaining $\boldsymbol{P}$ and $ \boldsymbol{A}$, sub-problem 2 can be solved by having the value of $ \boldsymbol{A}$. 
The sub-problem 1 is as follow
\max\limits_{\boldsymbol{P}, \boldsymbol{A} }   \quad &   \eta(\boldsymbol{P},\boldsymbol{A})\\
\text{subject to} \quad  & \bar{p}_{r_{(s,i)}} \leq P_{max} && \quad \forall s, \forall i,   \\
&p_{u_{(v,k)}}  \geq 0  &&\quad \forall v, \forall k, \\
&\mathcal{R}_{u_{(v,k)}} \geq  \mathcal{R}_{u_{(v,k)}}^{min} && \quad \forall v, \forall k, \\
&C_{r_{(s,i)}} \leq C_{r_{(s,i)}}^{max}  &&\quad \forall s, \forall i,\label{cc14} \\
&D_{s} \leq D_{s}^{max}  &&\quad \forall s, \label{cc15} \\
& \textstyle  \sum_{s=1}^{S}a_{v,s} \geq 1 &&\quad \forall s.
\label{constraints1}
In sub-problem 2, $ \boldsymbol{Y}$ is obtained. The sub-problem 2 is
\min\limits_{\boldsymbol{y} }   \quad &   \psi_{tot}(\boldsymbol{Y})\\
\text{s. t.} \quad & \textstyle \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{v,s} \geq 1\times\sum_{v=1}^{V}a_{v,s} \forall s, \\
 &\textstyle  \sum_{s=1}^{S} y_{s,d} \bar{\Omega}_{\mathfrak{z},s}^{tot}  \leq   \tau_{\mathfrak{z}_d}  \forall d,, \forall \mathfrak{z}\in \mathcal{E};  \label{eqomega}
\label{constraints2}

>>>>

\textstyle \phi_{tot} = \sum_{s=1}^{S}\phi_{s} + \sum_{d=1}^{D_c}z_d \psi_d .

@@

In addition, $\phi_{s,d}$ is obtained from below
\phi_{s} = M_s^u \phi_s^u + M_s^c \phi_s^c+ M_s^d \phi_s^d

@@

\min\limits_{\boldsymbol{P}, \boldsymbol{A}, \boldsymbol{E}, \boldsymbol{M}, \boldsymbol{G}, \boldsymbol{Y} }   \quad &  P_{tot}+ \varphi \phi_{tot} \ \\

@@

& \sum_{s=1}^{S}\sum_{v=1}^{V}\sum_{i=1}^{U_v}a_{u(v,i)}g^r_{u(v,i)}e^{k,s}_{r,u(v,i)} \leq 1 \quad \forall r, \label{c21} \\
&  \sum_{s=1}^{S}b_{v,s} \geq 1 \quad \forall v,\\

@@
